Recruiting Chapter

### 2020-12-19 manuscript.Rmd
updates to manuscript

[CRYSTAL, CAN YOU CLEAN UP THIS PARAGRAPH AND THE NEXT ONE; THESE PARAGRAPHS ARE TRANSITIONING FROM LIT REVIEW INTRODUCTION/BACKGROUND TO OUR PROJECT; AND ALSO MOTIVATING THE ANELYSES THAT WE DO; JUST USE YOUR JUDGMENT. THANK YOU!] Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities. Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges. <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->

Our analyses to date have focused only on visits by public research universities<!--[CITE]-->. The big-picture takeaways are as follows. Most public research universities in our sample made more out-of-state than in-state recruiting visits. The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps. Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas. Most public universities also made a disproportionate number of out-of-state visits to private high schools. In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools. Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.

Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges and universities in our sample, separated by event type and in-state vs. out-of-state. <!--TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... -->Table/Figure X demonstrates the disproportionate number of visits to private high schools. The goal of this chapter is to investigate off-campus recruiting visits to private high schools. Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.

<!--
WHAT TO SHOW IN TABLES/FIGURES:
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->

>>>>

Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year. The data collection sample comes from three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout 2017. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges. <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->

Our analyses to date have focused only on visits by public research universities<!--[CITE]-->. We found that most public research universities in our sample made more out-of-state than in-state recruiting visits. The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps. Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas. Most public universities also made a disproportionate number of out-of-state visits to private high schools, which tend to be more affluent and white. <!--In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools. Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.-->

These findings motivated the goal of this chapter to investigate off-campus recruiting visits to private high schools. Public research universities have the mission of providing social mobility, yet their large number of out-of-state visits to private high schools are making them more similar to private institutions. Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges/universities in our sample, respectively. A disproportionate number of out-of-state private high school visits can be seen for both public and private institutions. In this chapter, we will answer the research questions: Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.

<!--
TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools.

WHAT TO SHOW IN TABLES/FIGURES:
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->
